
# Import Library and Setup
```{r}
library(dplyr)
library(lubridate)
library(forecast)
library(TTR)
library(ggplot2)
library(tseries)
library(gridExtra)
```

# Data Import
```{r}
covid <- read.csv("D:/emotions/archive (1)/covid_19_indonesia_time_series_all.csv")
rmarkdown::paged_table(covid)
```
The data has 4,578 obs and 37 columns. 

#Data Preparation and EDA
```{r}
#subset the location only Jakarta, and column i..Date, and New.Cases and change data type
covid1 <- covid %>% 
  subset(Location == "DKI Jakarta") %>% 
  select(ï..Date, New.Cases) %>% 
  mutate(ï..Date = mdy(ï..Date)) 

#change the column name from i..Date to Date
colnames(covid1)[1] = "Date"
```
#After subset the data can’t contain NA (missing value)

```{r}
#Check if there is missing column in data
colSums(is.na(covid1))
```
The data in Maret is so much of 0 value, so we’ll use the data start from April..The data must be ordered by time.

```{r}
covid1 <- covid1 %>% 
  subset(Date >= "2020-04-01")
```
Then we’ll check when the data start and end.


```{r}
range(covid1$Date)
```
Now, our data is from April 1, 2020 to July 31, 2020. Then we’ll convert the data to ts object.


```{r}
#create object ts 
covid_ts <- ts(data = covid1$New.Cases,
   start = min(covid1$Date),
   frequency = 7) #weekly seasonality 

#visualise object covid_ts
covid_ts %>% autoplot()
```
From the plot, we can see that our data’s model is multiplicative. We’ll try to see the seasonality, trend and error of data.

```{r}
covid_dc <- decompose(covid_ts, type = "multiplicative")
covid_dc %>% autoplot()
```
We can also see an up or down trend using adjusted seasonal which has removing the effects of seasonal data.
```{r}
autoplot(covid_dc$x - covid_dc$seasonal)
```
From the plot and information above, we can see that the data’s seasonal pattern is random or no seasonal. The trend patterns of data is increasing.
